19th International Satisfiability Modulo Theories Competition (SMT-COMP 2024): Rules and Procedures

### 2024-05-24 rules/rules24.tex
Remove mention of the dockerfile

  \item {\bf Submission process.}  \emergencystretch.5cm
  We changed the submission process from a Google form to a push request to the
  SMT-COMP GitHub repository (\url{https://github.com/SMT-COMP/smt-comp.github.io/tree/master/submissions}).
  Detailed instructions can be found in the README file there.
  Moreover, participants are now required to upload their final solver versions as a Zenodo
  (\url{https://zenodo.org/}) submission that must contain a docker file that compiles the solver.
%
  \rationale{The change from Google form to GitHub push request makes it easier for us to
             automatically create scripts for BenchExec. The submission of the final solver
             versions to Zenodo makes it more likely that the competition results stay replicable.}

@@

\header{SMT Solver Submission.}
%
An entrant to SMT-COMP is a solver submitted by its authors via
a push request to the SMT-COMP GitHub repository (\url{https://github.com/SMT-COMP/smt-comp.github.io/tree/master/submissions}), or, for
\paralleltrack{} and \cloudtrack{}, otherwise communicated to the
organisers. The final solver version needs to be uploaded as a Zenodo (https://zenodo.org/ <https://zenodo.org/>) submission
that must contain a docker file that compiles the solver.

@@

\header{Participation in the Competition.}
%
For participation in SMT-COMP, the organizers must be informed of the solver's presence
\emph{and the tracks and divisions which it enters} via a push request
to the SMT-COMP GitHub repository
\begin{center}
  \url{https://github.com/SMT-COMP/smt-comp.github.io/tree/master/submissions}
\end{center}
The easiest way to create this push request is via the web-interface available under
the above URL. The actual solver must be submitted via a link to a publicly available
docker file that compiles the solver. For the \cloudtrack{} and \paralleltrack{},
it must be communicated separately to the organisers by email to
\href{mailto:aws-smtcomp-2024@googlegroups.com}{aws-smtcomp-2024@googlegroups.com}.
Note that independent of the tracks, the final solver version must be uploaded as a Zenodo
(https://zenodo.org/ <https://zenodo.org/>) submission.
Moreover, for each track, the submission must specify the logics which are
supported by the solver. The solver will enter all divisions where it
supports at least one logic. It is possible to submit specific configurations
of command line  options per track/logic/division as well as a default configuration
of command line options for all tracks/logics/divisions without their own configuration.
A submission \textbf{must} also include a link to the \emph{system description} (see below)
and a \emph{32-bit unsigned integer}. These integer numbers, collected from all
submissions, are used to seed competition tools.

>>>>

  \item {\bf Submission process.}  \emergencystretch.5cm
  We changed the submission process from a Google form to a push request to the
  SMT-COMP GitHub repository (\url{https://github.com/SMT-COMP/smt-comp.github.io/tree/master/submissions}).
  Detailed instructions can be found in the README file there.
  Moreover, participants are now required to upload their final solver versions as a Zenodo
  (\url{https://zenodo.org/}) submission.
%
  \rationale{The change from Google form to GitHub push request makes it easier for us to
             automatically create scripts for BenchExec. The submission of the final solver
             versions to Zenodo makes it more likely that the competition results stay replicable.}

@@

\header{SMT Solver Submission.}
%
An entrant to SMT-COMP is a solver submitted by its authors via
a push request to the SMT-COMP GitHub repository (\url{https://github.com/SMT-COMP/smt-comp.github.io/tree/master/submissions}), or, for
\paralleltrack{} and \cloudtrack{}, otherwise communicated to the
organisers. The final solver version needs to be uploaded as a Zenodo (https://zenodo.org/ <https://zenodo.org/>) submission. The solver is an archive that contains the executable precompiled (statically linked is preferable). It will be executed on a computer that have the same installation than the docker image \texttt{docker image name}.

@@

\header{Participation in the Competition.}
%
For participation in SMT-COMP, the organizers must be informed of the solver's presence
\emph{and the tracks and divisions which it enters} via a push request
to the SMT-COMP GitHub repository
\begin{center}
  \url{https://github.com/SMT-COMP/smt-comp.github.io/tree/master/submissions}
\end{center}
The easiest way to create this push request is via the web-interface available under
the above URL. For the \cloudtrack{} and \paralleltrack{},
it must be communicated separately to the organisers by email to
\href{mailto:aws-smtcomp-2024@googlegroups.com}{aws-smtcomp-2024@googlegroups.com}.
Note that independent of the tracks, the final solver version must be uploaded as a Zenodo
(https://zenodo.org/ <https://zenodo.org/>) submission.
Moreover, for each track, the submission must specify the logics which are
supported by the solver. The solver will enter all divisions where it
supports at least one logic. It is possible to submit specific configurations
of command line  options per track/logic/division as well as a default configuration
of command line options for all tracks/logics/divisions without their own configuration.
A submission \textbf{must} also include a link to the \emph{system description} (see below)
and a \emph{32-bit unsigned integer}. These integer numbers, collected from all
submissions, are used to seed competition tools.
